---
title: "Distance_Analysis_Fractals"
output:
  pdf_document:
    toc: yes
  html_notebook:
    code_folding: hide
    toc: yes
  html_document:
    code_folding: hide
    highlight: pygments
    theme: flatly
    toc: yes
---
# This notebook conducts the behavioral analyses for Representational integration and differentiation in the human hippocampus following goal directed navigation by Fernandez et al., 2023

Load Packages 
```{r load necessary packages and dataframe, warning=FALSE, message =FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(stringr)
library(lattice)
library(emmeans)
library(languageR)
library(performance)
library(effects)
library(Rmisc)
library(reshape)
library(tidyr)
library(ez)
library(car)
library(sjPlot)
```

# Load and clean data
```{r}
# load the data
df1 = read.csv('~/Dropbox/Project/analysis/mixedmodels/psa_longform_allSubs_vmpfc.csv',header = T)   # if on laptop
df2 = read.csv('~/Dropbox/Project/analysis/mixedmodels/psa_longform_allSubs_june2021.csv',header = T) # remove random column
df3 = read.csv('~/Dropbox/Project/analysis/mixedmodels/psa_longform_allSubs_controls.csv',header = T)
df2$X <- NULL

df = rbind(df1,df2,df3) # combine dfs

# data for brain/behav analysis requested by reviewer
df_trialwise = read.csv('~/Dropbox/Project/analysis/mixedmodels/HPC_PAPER/Finals_github/trialwiseModel.csv',header = T) 

# exclude data previously determined 
df <- df %>%
  filter(!(subNum == "17" & sesNum == "3"))

# figure color schemes
colors123 <- c('#76dfca', '#44999e', '#005a74')
colors12 <- c('#76dfca', '#44999e')
colors23 <- c('#44999e', '#005a74')
colors13 <- c('#76dfca','#005a74')
colorsbehav <- c('#a21a45', '#93003a') # '#d08c88', '#f4777f' '#f1aaa6'

# lists and names of things we will use later
vmpfc <- "vmPFC"
hpc_left = "Left hippocampus"
hpc_right = "Right Hippocampus"
hpc_all = "Bilateral Hippocampus"
hpcROIs <- c("HPC_left", "HPC_right")
ercROIs <- c("ERC_left", "ERC_right")

btwdists <- c("2 (within-context)","2 (across-contexts)")
wcdists <- c("1 (within-context)", "2 (within-context)")
acdists <- c("1 (across-contexts)","2 (across-contexts)", "3 (across-contexts)", "4 (across-contexts)")
```

Create new columns for comparisons of interest
```{r}
# get rid of this stupid space that is somehow in the csvs 
df$stim1_context[df$stim1_context=="hub "]="hub"
df$stim1_context=droplevels(df$stim1_context)

# clean up and factor subNum, sesNum
df$subNum <- sapply(df$subNum, function(x) sprintf('%.2d',x))
df$subNum <- factor(df$subNum)

# Add new column for stimtype comparison, factor the result
df$stimtype_comparison <- NA
df$stimtype_comparison[df$stim1_type == df$stim2_type] <- "within-stimulus category"
df$stimtype_comparison[df$stim1_type != df$stim2_type] <- "across-stimulus category"
df$stimtype_comparison[df$stim1_ID == df$stim2_ID] <- "self"
df$stimtype_comparison <- factor(df$stimtype_comparison, levels = c("self","within-stimulus category","across-stimulus category"))

# # Add new column for context comparison, factor the result
df$context_comparison <- NA
df$context_comparison[df$stim1_context == df$stim2_context] <- "within-context"
df$context_comparison[df$stim1_context != df$stim2_context] <- "across-contexts"
df$context_comparison[df$stim1_ID == df$stim2_ID] <- "self"
df$context_comparison <- factor(df$context_comparison, levels = c("self","within-context","across-contexts"))

# Add new column for distance comparisons (FRACTALS), factor the result
df <- df %>%
  filter(stim1_type == "FR", stim2_type == "FR")
```

```{r}
df$distance_comparison <- NA
df$distance_comparison[(df$stim1_context == df$stim2_context) & (df$distance == "1")] <- "1 (within-context)"
df$distance_comparison[(df$stim1_context == df$stim2_context) & (df$distance == "2")] <- "2 (within-context)"
df$distance_comparison[(df$stim1_context != df$stim2_context) & (df$distance == "1.5")] <- "1 (across-contexts)"
df$distance_comparison[(df$stim1_context != df$stim2_context) & (df$distance == "2.5")] <- "2 (across-contexts)"
df$distance_comparison[(df$stim1_context != df$stim2_context) & (df$distance == "3.5")] <- "3 (across-contexts)"
df$distance_comparison[(df$stim1_context != df$stim2_context) & (df$distance == "4")] <- "4 (across-contexts)"
df$distance_comparison[(df$stim1_context != df$stim2_context) & (df$distance == "4.5")] <- "4 (across-contexts)"
df$distance_comparison <- factor(df$distance_comparison, levels = c("1 (within-context)", "2 (within-context)", "1 (across-contexts)", "2 (across-contexts)", "3 (across-contexts)", "4 (across-contexts)"))

# Add new column for within-context distance comparison, factor the result
df$wcdistance <- NA
df$wcdistance[df$distance_comparison == "1 (within-context)"] <- "1"
df$wcdistance[df$distance_comparison == "2 (within-context)"] <- "2"
df$wcdistance <- factor(df$wcdistance)

# Add new column for across-contexts distance comparison, factor the result
df$acdistance <- NA
df$acdistance[df$distance_comparison == "1 (across-contexts)"] <- "1"
df$acdistance[df$distance_comparison == "2 (across-contexts)"] <- "2"
df$acdistance[df$distance_comparison == "3 (across-contexts)"] <- "3"
df$acdistance[df$distance_comparison == "4 (across-contexts)"] <- "4"
df$acdistance <- factor(df$acdistance)

# Add new column for renaming sesNum, factor the result
df$phase <- NA
df$phase[df$sesNum == "1"] <- "Pre-Learning"
df$phase[df$sesNum == "2"] <- "Post Local Navigation"
df$phase[df$sesNum == "3"] <- "Post Global Navigation"
df$phase <- factor(df$phase, levels = c("Pre-Learning", "Post Local Navigation", "Post Global Navigation"))
```

Subset data for distance models
```{r}
# Expand to all distances (within and across context), Still get rid of diagonal and only include within stimulus category comparisons
distance.ac.123 <- df %>%
  filter((stimtype_comparison != "self"),(stimtype_comparison == "within-stimulus category"))

# refactor everything
distance.ac.123$stimtype_comparison <- factor(distance.ac.123$stimtype_comparison, levels = c("within-stimulus category","across-stimulus category"))
distance.ac.123$context_comparison <- factor(distance.ac.123$context_comparison, levels = c("within-context","across-contexts"))
distance.ac.123$subNum <- factor(distance.ac.123$subNum)
distance.ac.123$sesNum <- factor(distance.ac.123$sesNum)

### Set contrasts appropriately ###
# make a copy of the data
distance.ac.123.copy <- data.frame(distance.ac.123)

# sum coding for stimtype_comparison, context comparison, stim type, hub comparison, posCat comparison
contrasts(distance.ac.123.copy$stimtype_comparison) <- c(0.5,-0.5)
colnames(attr(distance.ac.123.copy$stimtype_comparison,"contrasts")) = "within>across"
contrasts(distance.ac.123.copy$context_comparison) <- c(0.5,-0.5)
colnames(attr(distance.ac.123.copy$context_comparison,"contrasts")) = "within>across"
```

### Bilateral hippocampus

#### Landmarks, within and across tracks
Plot mean pattern similarity for landmarks across all three sessions for all distance categories
```{r, fig.width=5, fig.height=2.5}
distance.ac.123.hpc_all.LM <- distance.ac.123.copy %>%
  filter(roi %in% hpcROIs, stim1_type == "FR",distance_comparison!="NA")

# within context distances
wc123.test <- distance.ac.123.hpc_all.LM %>%
  filter(distance_comparison %in% wcdists)

summary.wc123.test.r <- summarySEwithin(data = wc123.test, measurevar = "fisher_r", withinvars = c("phase","stim1_type", "wcdistance"),idvar = 'subNum')
summary.wc123.test.r.sub <- summarySEwithin(data = wc123.test, measurevar = "fisher_r", withinvars = c("subNum","phase","stim1_type", "wcdistance"))

# across context all scans 
ac123.test <- distance.ac.123.hpc_all.LM %>%
  filter(distance_comparison %in% acdists)

summary.ac123.test.r <- summarySEwithin(data = ac123.test, measurevar = "fisher_r", withinvars = c("phase","stim1_type", "acdistance"),idvar = 'subNum')
summary.ac123.test.r.sub <- summarySEwithin(data = ac123.test, measurevar = "fisher_r", withinvars = c("subNum","phase","stim1_type", "acdistance"))
```

```{r,fig.width=5, fig.height=2}
withindist_hpc_r <- ggplot() + 
  #geom_point(data=summary.wc123.test.r.sub, aes(y=fisher_r,x=wcdistance,group=phase), alpha = .5, size = .5, position = position_dodge(0.05)) +
  geom_errorbar(data=summary.wc123.test.r, aes(y=fisher_r, x=wcdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.wc123.test.r, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.wc123.test.r, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf(hpc_all)) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
withindist_hpc_r
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/HPC_within_distance.png', withindist_hpc_r, dpi=600)

acrossdist_hpc_r <- ggplot() + 
  #geom_point(data=summary.ac123.test.r.sub, aes(y=fisher_r,x=acdistance,group=phase), alpha = .5, size = .5, position = position_dodge(0.05)) +
  geom_errorbar(data=summary.ac123.test.r, aes(y=fisher_r, x=acdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.ac123.test.r, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.ac123.test.r, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf(hpc_all)) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
acrossdist_hpc_r
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/HPC_across_distance.png', acrossdist_hpc_r, dpi=600)
```

### Interaction with performance metric
Median path efficiency at start of day 2 Global Nav task 
```{r}
ac.distances.2.hpc_all <- distance.ac.123.copy %>%
  filter(roi %in% hpcROIs, stim1_type == "FR",distance_comparison %in% acdists,sesNum == "2")
ac.distances.2.hpc_all$subNum <- factor(ac.distances.2.hpc_all$subNum)

# add a path inefficiency metric to look at this in a continuous manner 
# (note to self: learn r)
ac.distances.2.hpc_all <- ac.distances.2.hpc_all %>%
  mutate(d2_startruns_meanefficiency = ifelse(subNum == "02",82.986,ifelse(subNum == "03",12.747,ifelse(subNum == "05",68.736,ifelse(subNum == "06",26.819,
                                       ifelse(subNum == "08",24.125,ifelse(subNum == "09",32.540,ifelse(subNum == "10",40.703,ifelse(subNum == "12",9.414,
                                       ifelse(subNum == "13",134.297,ifelse(subNum == "16",40.677,ifelse(subNum == "18",5.652,ifelse(subNum == "19",31.473,
                                       ifelse(subNum == "20",17.521,ifelse(subNum == "21",19.862,ifelse(subNum == "22",14.135,ifelse(subNum == "25",78.217,
                                       ifelse(subNum == "28",8.289,ifelse(subNum == "29", 62.499,ifelse(subNum == "31", 82.715, ifelse(subNum == "32", 14.708,
                                       ifelse(subNum == "33",101.120,"ignore")))))))))))))))))))))) %>%
  filter(d2_startruns_meanefficiency!="ignore")

ac.distances.2.hpc_all <- ac.distances.2.hpc_all %>%
  mutate(d2_startruns_medefficiency = ifelse(subNum == "02", 43.807,ifelse(subNum == "03", 8.866,ifelse(subNum == "05", 72.640,ifelse(subNum == "06", 15.123,
                                      ifelse(subNum == "08", 15.205,ifelse(subNum == "09", 10.599,ifelse(subNum == "10", 25.187,ifelse(subNum == "12", 4.720,
                                      ifelse(subNum == "13", 91.166,ifelse(subNum == "16", 27.476,ifelse(subNum == "18", 4.173,ifelse(subNum == "19", 16.707,
                                      ifelse(subNum == "20", 7.674,ifelse(subNum == "21", 7.693,ifelse(subNum == "22", 3.153,ifelse(subNum == "25", 29.181,
                                      ifelse(subNum == "28", 0.427,ifelse(subNum == "29", 50.230,ifelse(subNum == "31", 73.830, ifelse(subNum == "32", 10.177, 
                                      ifelse(subNum == "33", 90.895,"ignore")))))))))))))))))))))) %>%
  filter(d2_startruns_medefficiency!="ignore")

ac.distances.2.hpc_all$d2_startruns_meanefficiency <- as.numeric(ac.distances.2.hpc_all$d2_startruns_meanefficiency) 
ac.distances.2.hpc_all$d2_startruns_medefficiency <- as.numeric(ac.distances.2.hpc_all$d2_startruns_medefficiency) 

model.ac.distances.2.hpc_all.cont_med <- lmer(fisher_r ~ distance*d2_startruns_medefficiency + (1 | subNum),
                                     data = ac.distances.2.hpc_all,
                                     control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.2.hpc_all.cont_med)
```

```{r}
tab_model(model.ac.distances.2.hpc_all.cont_med, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

Day 3-
```{r}
ac.distances.3.hpc_all <- distance.ac.123.copy %>%
  filter(roi %in% hpcROIs, stim1_type == "FR",distance_comparison %in% acdists,sesNum == "3")
ac.distances.3.hpc_all$subNum <- factor(ac.distances.3.hpc_all$subNum)

# add a path inefficiency metric to look at this in a continuous manner 
# (note to self: learn r)
ac.distances.3.hpc_all <- ac.distances.3.hpc_all %>%
  mutate(d2_startruns_medefficiency = ifelse(subNum == "02", 43.807,ifelse(subNum == "03", 8.866,ifelse(subNum == "05", 72.640,ifelse(subNum == "06", 15.123,
                                      ifelse(subNum == "08", 15.205,ifelse(subNum == "09", 10.599,ifelse(subNum == "10", 25.187,ifelse(subNum == "12", 4.720,
                                      ifelse(subNum == "13", 91.166,ifelse(subNum == "16", 27.476,ifelse(subNum == "18", 4.173,ifelse(subNum == "19", 16.707,
                                      ifelse(subNum == "20", 7.674,ifelse(subNum == "21", 7.693,ifelse(subNum == "22", 3.153,ifelse(subNum == "25", 29.181,
                                      ifelse(subNum == "28", 0.427,ifelse(subNum == "29", 50.230,ifelse(subNum == "31", 73.830, ifelse(subNum == "32", 10.177, 
                                      ifelse(subNum == "33", 90.895,"ignore")))))))))))))))))))))) %>%
  filter(d2_startruns_medefficiency!="ignore")

ac.distances.3.hpc_all$d2_startruns_medefficiency <- as.numeric(ac.distances.3.hpc_all$d2_startruns_medefficiency) 

model.ac.distances.3.hpc_all.cont_med <- lmer(fisher_r ~ distance*d2_startruns_medefficiency 
                                     + (1 | subNum),
                                     data = ac.distances.3.hpc_all,
                                     control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.3.hpc_all.cont_med)
```

```{r}
tab_model(model.ac.distances.3.hpc_all.cont_med, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

Day 1
```{r}
ac.distances.1.hpc_all <- distance.ac.123.copy %>%
  filter(roi %in% hpcROIs, stim1_type == "FR",distance_comparison %in% acdists,sesNum == "1")
ac.distances.1.hpc_all$subNum <- factor(ac.distances.1.hpc_all$subNum)

# add a path inefficiency metric to look at this in a continuous manner 
# (note to self: learn r)
ac.distances.1.hpc_all <- ac.distances.1.hpc_all %>%
  mutate(d2_startruns_medefficiency = ifelse(subNum == "02", 43.807,ifelse(subNum == "03", 8.866,ifelse(subNum == "05", 72.640,ifelse(subNum == "06", 15.123,
                                      ifelse(subNum == "08", 15.205,ifelse(subNum == "09", 10.599,ifelse(subNum == "10", 25.187,ifelse(subNum == "12", 4.720,
                                      ifelse(subNum == "13", 91.166,ifelse(subNum == "16", 27.476,ifelse(subNum == "18", 4.173,ifelse(subNum == "19", 16.707,
                                      ifelse(subNum == "20", 7.674,ifelse(subNum == "21", 7.693,ifelse(subNum == "22", 3.153,ifelse(subNum == "25", 29.181,
                                      ifelse(subNum == "28", 0.427,ifelse(subNum == "29", 50.230,ifelse(subNum == "31", 73.830, ifelse(subNum == "32", 10.177, 
                                      ifelse(subNum == "33", 90.895,"ignore")))))))))))))))))))))) %>%
  filter(d2_startruns_medefficiency!="ignore")

ac.distances.1.hpc_all$d2_startruns_medefficiency <- as.numeric(ac.distances.1.hpc_all$d2_startruns_medefficiency) 

model.ac.distances.1.hpc_all.cont_med <- lmer(fisher_r ~ distance*d2_startruns_medefficiency
                                     + (1 | subNum),
                                     data = ac.distances.1.hpc_all,
                                     control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.1.hpc_all.cont_med)
```

```{r}
tab_model(model.ac.distances.1.hpc_all.cont_med, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

##### Split HPC into different groups to model
First, look within track

```{r, fig.width=3, fig.height=2.5}
contrasts(wc123.test$wcdistance) <- c(-0.5,0.5)
colnames(attr(wc123.test$wcdistance,"contrasts")) = "LD2>LD1"


model.wc.distances.123.hpc_all <- lmer(fisher_r ~ sesNum*wcdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = wc123.test,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.wc.distances.123.hpc_all)
contrasts.wc.distances.123.hpc_all <- emmeans(model.wc.distances.123.hpc_all, specs = pairwise~sesNum:wcdistance)
contrasts.wc.distances.123.hpc_all
```

```{r}
tab_model(model.wc.distances.123.hpc_all, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

Next, look at across tracks, link dist 2 3 4
model all 3 days- distance, continuous variable
```{r}
ac.distances.123.hpc_all <- distance.ac.123.copy %>%
  filter(roi %in% hpcROIs, stim1_type == "FR",distance_comparison %in% acdists)
ac.distances.123.hpc_all$subNum <- factor(ac.distances.123.hpc_all$subNum)
ac.distances.123.hpc_all$acdistance <- as.integer(ac.distances.123.hpc_all$acdistance)

model.ac.distances.123.hpc_all <- lmer(fisher_r ~ sesNum*acdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = ac.distances.123.hpc_all,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.123.hpc_all)
```

```{r}
tab_model(model.ac.distances.123.hpc_all, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

### VMPFC
```{r, fig.width=5, fig.height=2}
wc.distances.123.vmpfc <- distance.ac.123.copy %>%
  filter(roi == "VMPFC",stim1_type == "FR", distance_comparison %in% wcdists)

summary.wc.distances.123.vmpfc <- summarySEwithin(data = wc.distances.123.vmpfc, measurevar = "fisher_r", 
                                                      withinvars = c("phase","stim1_type","wcdistance"),idvar = 'subNum')

withindist_vmpfc <- ggplot() + 
  geom_errorbar(data=summary.wc.distances.123.vmpfc, aes(y=fisher_r, x=wcdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.wc.distances.123.vmpfc, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.wc.distances.123.vmpfc, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf("vmPFC")) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
withindist_vmpfc
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/vmpfc_within_distance.png', withindist_vmpfc, dpi=600)
```

Plot mean pattern similarity for landmarks across all three sessions for all distance categories
```{r, fig.width=5, fig.height=2}
distance.ac.123.vmpfc.LM <- distance.ac.123.copy %>%
  filter(roi == "VMPFC", stim1_type == "FR",distance_comparison%in% acdists)

summary.distance.ac.123.vmpfc.LM <- summarySEwithin(data = distance.ac.123.vmpfc.LM, measurevar = "fisher_r", 
                                                      withinvars = c("phase","stim1_type","acdistance"),idvar = 'subNum')

vmpfc_across_distance <- ggplot() + 
  geom_errorbar(data=summary.distance.ac.123.vmpfc.LM, aes(y=fisher_r, x=acdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.distance.ac.123.vmpfc.LM, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.distance.ac.123.vmpfc.LM, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf(vmpfc)) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
vmpfc_across_distance
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/vmpfc_across_distance.png', vmpfc_across_distance, dpi=600)
```

##### Split vmpfc into different groups to model
First, look within track
```{r}
model.wc.distances.123.vmpfc <- lmer(fisher_r ~ sesNum*wcdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = wc.distances.123.vmpfc,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.wc.distances.123.vmpfc)
contrasts.wc.distances.123.vmpfc <- emmeans(model.wc.distances.123.vmpfc, specs = pairwise~sesNum:wcdistance)
```

```{r}
tab_model(model.wc.distances.123.vmpfc, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

Next, look at across tracks, link distance 2 3 4
model all 3 days- distance, continuous variable
```{r}
ac.distances.123.vmpfc <- distance.ac.123.copy %>%
  filter(roi == "VMPFC", stim1_type == "FR",distance_comparison %in% acdists)
ac.distances.123.vmpfc$subNum <- factor(ac.distances.123.vmpfc$subNum)

summary.ac.distances.123.vmpfc <- summarySEwithin(data = ac.distances.123.vmpfc, measurevar = "fisher_r", 
                                                      withinvars = c("sesNum","stim1_type","distance_comparison"),idvar = 'subNum')

model.ac.distances.123.vmpfc <- lmer(fisher_r ~ sesNum*distance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = ac.distances.123.vmpfc,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.123.vmpfc)
```

```{r}
tab_model(model.ac.distances.123.vmpfc, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

## Calcarine
Plot mean pattern similarity for landmarks across all three sessions for all distance categories
```{r, fig.width=5, fig.height=2.5}
distance.ac.123.calc.LM <- distance.ac.123.copy %>%
  filter(roi == "Calcarine", stim1_type == "FR",distance_comparison!="NA")

# within context distances
wc123.test <- distance.ac.123.calc.LM %>%
  filter(distance_comparison %in% wcdists)

# across context all scans 
ac123.test <- distance.ac.123.calc.LM %>%
  filter(distance_comparison %in% acdists)

summary.ac123.test.r <- summarySEwithin(data = ac123.test, measurevar = "fisher_r", withinvars = c("phase","stim1_type", "acdistance"),idvar = 'subNum')
summary.ac123.test.r.sub <- summarySEwithin(data = ac123.test, measurevar = "fisher_r", withinvars = c("subNum","phase","stim1_type", "acdistance"))
```

```{r,fig.width=5, fig.height=2}
acrossdist_control <- ggplot() + 
  #geom_point(data=summary.ac123.test.r.sub, aes(y=fisher_r,x=acdistance,group=phase), alpha = .5, size = .5, position = position_dodge(0.05)) +
  geom_errorbar(data=summary.ac123.test.r, aes(y=fisher_r, x=acdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.ac123.test.r, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.ac123.test.r, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf("Calcarine")) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
acrossdist_control
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/control_across_distance.png', acrossdist_control, dpi=600)
```

within track
```{r, fig.width=3, fig.height=2.5}
wc.distances.123.calc <- distance.ac.123.copy %>%
  filter(roi == "Calcarine",stim1_type == "FR", distance_comparison %in% wcdists)

summary.wc.distances.123.calc <- summarySEwithin(data = wc.distances.123.calc, measurevar = "fisher_r", withinvars = c("phase","stim1_type", "wcdistance"),idvar = 'subNum')
```

```{r}
contrasts(wc123.test$wcdistance) <- c(-0.5,0.5)
colnames(attr(wc123.test$wcdistance,"contrasts")) = "LD2>LD1"


model.wc.distances.123.calc <- lmer(fisher_r ~ sesNum*wcdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = wc123.test,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.wc.distances.123.calc)
contrasts.wc.distances.123.calc <- emmeans(model.wc.distances.123.calc, specs = pairwise~sesNum:wcdistance)
```
```{r}
tab_model(model.wc.distances.123.calc, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

Next, look at across tracks, link distance 2 3 4
model all 3 days- distance, continuous variable
```{r}
ac.distances.123.calc <- distance.ac.123.copy %>%
  filter(roi == "Calcarine", stim1_type == "FR",distance_comparison %in% acdists)
ac.distances.123.calc$subNum <- factor(ac.distances.123.calc$subNum)

summary.ac.distances.123.calc <- summarySEwithin(data = ac.distances.123.calc, measurevar = "fisher_r", 
                                                      withinvars = c("sesNum","stim1_type","distance_comparison"),idvar = 'subNum')

model.ac.distances.123.calc <- lmer(fisher_r ~ sesNum*distance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = ac.distances.123.calc,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.123.calc)
```

```{r}
tab_model(model.ac.distances.123.calc, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

### EC
#### Test for hemispheric differences
Within track only
```{r}
distance.wc.123.erc_all.LM <- distance.ac.123.copy %>%
  filter(roi %in% ercROIs,stim1_type == "FR", distance_comparison!="NA", wcdistance != "NA")
contrasts(distance.wc.123.erc_all.LM$wcdistance) <- c(-0.5,0.5)
colnames(attr(distance.wc.123.erc_all.LM$wcdistance,"contrasts")) = "LD2>LD1"

model.distance.wc.123.erc_all <- lmer(fisher_r ~ sesNum*wcdistance*roi + stim1_avgAct + stim2_avgAct
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = distance.wc.123.erc_all.LM,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))
summary(model.distance.wc.123.erc_all)
```

```{r}
tab_model(model.distance.wc.123.erc_all, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

Across track only
```{r}
distance.ac.123.erc_all.LM <- distance.ac.123.copy %>%
  filter(roi %in% ercROIs,stim1_type == "FR", distance_comparison!="NA", acdistance != "NA") 
distance.ac.123.erc_all.LM$acdistance <- as.numeric(distance.ac.123.erc_all.LM$acdistance)

model.distance.ac.123.erc_all <- lmer(fisher_r ~ sesNum*acdistance*roi + stim1_avgAct + stim2_avgAct
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = distance.ac.123.erc_all.LM,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))
summary(model.distance.ac.123.erc_all)
```

```{r}
tab_model(model.distance.ac.123.erc_all, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

#### ERC_left within track
Plot mean pattern similarity for landmarks across all three sessions for all distance categories
```{r, fig.width=5, fig.height=2.5}
distance.ac.123.erc_left.LM <- distance.ac.123.copy %>%
  filter(roi =="ERC_left", stim1_type == "FR",distance_comparison!="NA")

distance.ac.123.erc_right.LM <- distance.ac.123.copy %>%
  filter(roi =="ERC_right", stim1_type == "FR",distance_comparison!="NA")

# within context distances 
wc123.test.erc_L <- distance.ac.123.erc_left.LM %>%
  filter(distance_comparison %in% wcdists)

summary.wc123.test.r.erc_L <- summarySEwithin(data = wc123.test.erc_L, measurevar = "fisher_r", withinvars = c("phase","stim1_type", "wcdistance"),idvar = 'subNum')

wc123.test.erc_R <- distance.ac.123.erc_right.LM %>%
  filter(distance_comparison %in% wcdists)

summary.wc123.test.r.erc_R <- summarySEwithin(data = wc123.test.erc_R, measurevar = "fisher_r", withinvars = c("phase","stim1_type", "wcdistance"),idvar = 'subNum')
```

```{r,fig.width=5, fig.height=2}
withindist_erc_L <- ggplot() + 
  geom_errorbar(data=summary.wc123.test.r.erc_L, aes(y=fisher_r, x=wcdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.wc123.test.r.erc_L, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.wc123.test.r.erc_L, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf("Left Entorhinal Cortex")) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
withindist_erc_L
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/ercL_within_distance.png', withindist_erc_L, dpi=600)

withindist_erc_R <- ggplot() + 
  geom_errorbar(data=summary.wc123.test.r.erc_R, aes(y=fisher_r, x=wcdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.wc123.test.r.erc_R, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.wc123.test.r.erc_R, aes(y=fisher_r,x=wcdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf("Right Entorhinal Cortex")) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
withindist_erc_R
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/ercR_within_distance.png', withindist_erc_R, dpi=600)
```

##### Split ERC into different groups to model for within track
ERC LEFT
```{r, fig.width=3, fig.height=2.5}
contrasts(wc123.test.erc_L$wcdistance) <- c(-0.5,0.5)
colnames(attr(wc123.test.erc_L$wcdistance,"contrasts")) = "LD2>LD1"


model.wc.distances.123.erc_left <- lmer(fisher_r ~ sesNum*wcdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = wc123.test.erc_L,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.wc.distances.123.erc_left)
contrasts.wc.distances.123.erc_left <- emmeans(model.wc.distances.123.erc_left, specs = pairwise~sesNum:wcdistance)
contrasts.wc.distances.123.erc_left
```

```{r}
tab_model(model.wc.distances.123.erc_left, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

ERC RIGHT
```{r, fig.width=3, fig.height=2.5}
contrasts(wc123.test.erc_R$wcdistance) <- c(-0.5,0.5)
colnames(attr(wc123.test.erc_R$wcdistance,"contrasts")) = "LD2>LD1"


model.wc.distances.123.erc_right <- lmer(fisher_r ~ sesNum*wcdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = wc123.test.erc_R,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.wc.distances.123.erc_right)
contrasts.wc.distances.123.erc_right <- emmeans(model.wc.distances.123.erc_right, specs = pairwise~sesNum:wcdistance)
contrasts.wc.distances.123.erc_right
```

```{r}
tab_model(model.wc.distances.123.erc_right, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```

#### Bilateral EC for across track model 
Next, look at across track 2 3 4
model all 3 days- distance, continuous variable
```{r}
ac.distances.123.erc_all <- distance.ac.123.copy %>%
  filter(roi %in% ercROIs, stim1_type == "FR",distance_comparison %in% acdists)
ac.distances.123.erc_all$subNum <- factor(ac.distances.123.erc_all$subNum)
ac.distances.123.erc_all$acdistance <- as.integer(ac.distances.123.erc_all$acdistance)

model.ac.distances.123.erc_all <- lmer(fisher_r ~ sesNum*acdistance
                       + stim1_avgAct + stim2_avgAct + v1_similarity + IT_similarity
                       + (1 + sesNum + stim1_avgAct + stim2_avgAct | subNum),
                       data = ac.distances.123.erc_all,
                       control = lmerControl(optimizer = "bobyqa",calc.derivs=FALSE))

summary(model.ac.distances.123.erc_all)
```

```{r,fig.width=5, fig.height=2}
summary.distance.ac.123.erc.LM <- summarySEwithin(data = ac.distances.123.erc_all, measurevar = "fisher_r", 
                                                      withinvars = c("phase","stim1_type","acdistance"),idvar = 'subNum')

summary.distance.ac.123.erc.LM.sub <- summarySEwithin(data = ac.distances.123.erc_all, measurevar = "fisher_r", 
                                                      withinvars = c("subNum","phase","stim1_type","acdistance"))

erc_across_distance <- ggplot() + 
  geom_errorbar(data=summary.distance.ac.123.erc.LM, aes(y=fisher_r, x=acdistance, group=phase,color=phase,ymin=fisher_r-se,ymax=fisher_r+se),size =1,width=.1, position = position_dodge(0.05)) +
  geom_line(data=summary.distance.ac.123.erc.LM, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 1.5) +
  geom_point(data=summary.distance.ac.123.erc.LM, aes(y=fisher_r,x=acdistance,group=phase,color=phase), size = 3, position = position_dodge(0.05)) +
  ggtitle(label = sprintf("Bilateral Entorhinal Cortex")) + 
  scale_fill_manual(values = colors123)+
  scale_color_manual(values = colors123)+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size=16),
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size=14),
        strip.text = element_text(size=13),
        panel.border = element_rect(color="black",fill=NA),
        legend.position = "None") +  
  ylab("Mean Pattern Similarity")+
  xlab("Link Distance")+
  labs(color="Study Phase")+
  facet_wrap(~phase)
erc_across_distance
#ggsave(filename = '~/Dropbox/Project/writing/HPC_Paper/figures/erc_across_distance.png', erc_across_distance, dpi=600)
```

```{r}
tab_model(model.ac.distances.123.erc_all, digits = 3,show.se = TRUE,show.stat = TRUE,show.ci =FALSE)
```
